Operation Mode Study in Cloud Manufacturing Ecosystem

### 2016-09-10 head.tex
tao's comment
shorten the abstract near 100 words

\begin{abstract}
In cloud manufacturing, individuals engage in manufacturing business through a well-designed platform, where the operator is able to manage distributed massive manufacturing resources.
Cloud manufacturing ecosystem has more complicated relationship among individuals in it than that in normal manufacturing system, one individual can make decisions depend on the surroundings and others'. In this paper, we designed an original operation mode with 3 extensions named incubation, outsourcing and metabolism for the ecosystem. We designed an agent-based simulation model to validate the effectiveness of these modes. Experiment result shows evolution in ecosystem: with incubation mode, the job queue length is reduced and the resource idle rate is declined; with outsourcing mode, the job queue length is also reduced but not as much as that with incubation mode and more resource is required; with metabolism mode, lower resource is required than that with other modes and resource idle rate just rose up a little.

@@

\begin{keyword}
Cloud manufacturing ecosystem \sep
Decision-making\sep
Operation mode\sep
Ecosystem evolution\sep
Agent-based simulation

>>>>

\begin{abstract}
In cloud manufacturing, platform operator is able to manage distributed massive manufacturing resources for manufacturing business.
Cloud manufacturing ecosystem has more complicated relationship among individuals than that in existing manufacturing system, every individual makes decisions depend on enriched information. In this paper, an original operation mode with three extensions namely incubation, outsourcing and metabolism mode are proposed. We designed an agent-based simulation model and the validation experiment result shows platform have: 1) shorter job queue length and lower resource idle rate with incubation mode; 2) a little shorter job queue length and fewer amount of registered resource with outsourcing mode; 3) the fewest amount of registered resource but a little higher resource idle rate with metabolism mode.

@@

\begin{keyword}
Cloud manufacturing ecosystem \sep
decision-making\sep
operation mode\sep
ecosystem evolution\sep
agent-based simulation
